Hamiltonian Mechanics unter besonderer Ber\"ucksichtigung der h\"ohreren Lehranstalten

### 2017-03-03 LTF.tex
add trapdoor functions

Lossy trapdoor functions are proved to be very usefull for the construction of CCA-secure encryption scheme. 
There already exists many efficient constructions of all-but-one lossy trapdoor functions with various assumptions~\cite{DBLP:journals/siamcomp/PeikertW11, DBLP:conf/crypto/BoldyrevaFO08}

@@

\end{section}

>>>>

Lossy trapdoor functions are proved to be very usefull for the construction of CCA-secure encryption scheme. 
There already exists many efficient constructions of all-but-one lossy trapdoor functions with various assumptions~\cite{DBLP:journals/siamcomp/PeikertW11, DBLP:conf/crypto/BoldyrevaFO08}.

The main idea of the lossy trapdoor function is that, it can be operated in two modes: Injective mode and lossy mode.

@@

  \begin{definition}
    A lossy trapdoor function $LTF$ with domain $Dom$ consits of the following algorithms $LTF = (\KeyGen, \Eval, \Inv, \LKeyGen)$:
    \begin{description}
    \item[${\mathsf{\KeyGen}}$] :
      \begin{enumerate}
        \item $LTF.\KeyGen(1^\lambda)$
      \end{enumerate}
    \item[${\mathsf{\Eval}}$] :
    \item[${\mathsf{\Inv}}$] :
    \item[${\mathsf{\LKeyGen}}$] :
    \end{description}
  \end{definition}
\end{section}
